Flowers text analysis

### 2022-10-13 code/annotation_analysis.Rmd
poke at analysis of end game labels

>>>>

# Within end-stuff

```{r}
sbert_post_test <- read_csv(here(annotation_path,"post_test.csv")) %>% bind_cols(readRDS(here(annotation_path,'post_sbert_post_test.RData')))  %>% as_tibble()

F_mat <- sbert_post_test %>% select(starts_with("...")) %>% as.matrix() #Features
M_mat <- sbert_post_test %>% select(-starts_with("...")) %>% mutate(feature_ind=row_number(), flower=str_c(color,num))
```

## Within flower
```{r}

end_distinctive <- M_mat %>% 
  group_by(flower, color) %>% 
  mutate(combinedId=str_c(gameId,"_",seen)) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, c("gameId1", "seen1")) |> 
  separate(dim2, c("gameId2", "seen2")) |> 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  ungroup()
```

end_distinctive |> mutate(same_group=ifelse(gameId1==gameId2, 
                                            "same_group","different_group"),
                          same_color=case_when(
  seen1=="own" & seen2=="own" ~ "own",
  seen2=="other" & seen1=="other" ~ "other",
  T ~"mixed"
))|> ggplot(aes(group=flower, x=color, y=sim, color=str_c(same_group,same_color)))+     
  stat_summary(aes(group=str_c(same_group, same_color)),fun.data = "mean_cl_boot", position = position_dodge(width=.3), geom="pointrange")

```
This is really poorly labelled. Needs stats.

## Between flowers
```{r}

end_between <- M_mat %>% 
  group_by(color) %>% 
  mutate(combinedId=str_c(playerId, "_",gameId,"_",seen, "_", flower)) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, c("player1","gameId1", "seen1" ,"flower1")) |> 
  separate(dim2, c("player2", "gameId2", "seen2", "flower2")) |> 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  filter(flower1!=flower2) |> 
  ungroup()
```

end_between |> mutate(same_group=case_when(
  player1==player2 ~ "same_person",
  gameId1==gameId2 ~ "same_group",
  T ~ "diferent_group"
), same_color=case_when(
  seen1=="own" & seen2=="own" ~ "own",
  seen2=="other" & seen1=="other" ~ "other",
  T ~"mixed"
))|> ggplot(aes(x=color, y=sim, color=str_c(same_group,same_color)))+     
  stat_summary(aes(group=str_c(same_group, same_color)),fun.data = "mean_cl_boot", position = position_dodge(width=.3), geom="pointrange")+facet_grid(.~same_group)

# TODO: between game & end-game
